Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-09-02 paper/ms.tex
Updated the way we do the software command upon receiving advice from the editor.

\software{Flash \citep{Fryxetal00,calder.curtis.ea:high-performance,calder.fryxell.ea:on,flash_pragmatic,flash_evolution} (\url{http://flash.uchicago.edu/}), 
MESA \citep{mesa1,mesa2,mesa3,mesa3e} (\url{http://mesa.sourceforge.net/}),
The
Helmholtz EOS table used in \CASTRO\ is available in the public BoxLib
Microphysics repository at
  (\url{https://github.com/BoxLib-Codes/Microphysics.git}, commit
  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).
}

>>>>

%\software{Flash \citep{Fryxetal00,calder.curtis.ea:high-performance,calder.fryxell.ea:on,flash_pragmatic,flash_evolution} (\url{http://flash.uchicago.edu/}), 
%MESA \citep{mesa1,mesa2,mesa3,mesa3e} (\url{http://mesa.sourceforge.net/}),
%The Helmholtz EOS table used in \CASTRO\ is available in the public BoxLib
%Microphysics repository at
%  (\url{https://github.com/BoxLib-Codes/Microphysics.git}, commit
%  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$),
%  Matplotlib (\url{http://dx.doi.org/10.5281/zenodo.44579}).
%}

\software{Flash \citep{Fryxetal00,calder.curtis.ea:high-performance,calder.fryxell.ea:on,flash_pragmatic,flash_evolution} (\url{http://flash.uchicago.edu/}), 
MESA \citep{mesa1,mesa2,mesa3,mesa3e} (\url{http://mesa.sourceforge.net/}),
The Helmholtz EOS table used in \CASTRO\ \citep{timmes.swesty:accuracy}, Available in the public BoxLib
Microphysics repository at
  (\url{https://github.com/BoxLib-Codes/Microphysics.git}, commit
  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$),
  Matplotlib (\url{http://dx.doi.org/10.5281/zenodo.44579}).
}
